Impact of Reviews and Ratings on Airbnb Pricing in Canada: Analyzing Information Dynamics

### 2024-02-15 outputs/paper/paper.qmd
Removed unnecessary files.

Our paper will follow a replication of research conducted by @citepaper on the effects of information on ethnic discrimination in the Airbnb market. We follow their paper to replicate the following aspects of the paper (1) the platform is effective in supplying useful information, so reviews and ratings impact the expectations of consumers and (2) there is a relationship between number of reviews and listed price. Data analysis for this reproduction is performed in `R` [@citeR], and additional help is provided by libraries such as `dplyr` [@dplyr], `ggplot2` [@ggplot], `ggrepel` [@ggrepel], `tidyverse` [@thereferencecanbewhatever], `kableExtra` [@kableextra], `knitr` [@knitr], `haven` [@haven], 'readr' [@readr], `stargazer`[@stargazer], `psych` [@psych], `scales` [@scales], `RColorBrewer` [@rcolorbrewer], `gridExtra` [@gridextra], `here` [@here].

>>>>

Our paper will follow a replication of research conducted by @citepaper on the effects of information on ethnic discrimination in the Airbnb market. We follow their paper to replicate the following aspects of the paper (1) the platform is effective in supplying useful information, so reviews and ratings impact the expectations of consumers and (2) there is a relationship between number of reviews and listed price. Data analysis for this reproduction is performed in `R` [@citeR], and additional help is provided by libraries such as `dplyr` [@dplyr], `ggplot2` [@ggplot], `ggrepel` [@ggrepel], `tidyverse` [@thereferencecanbewhatever], `kableExtra` [@kableextra], `knitr` [@knitr], `haven` [@haven], `readr` [@readr], `stargazer`[@stargazer], `psych` [@psych], `scales` [@scales], `RColorBrewer` [@rcolorbrewer], and `gridExtra` [@gridextra], `here` [@here].
